Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-07-04 paper/IJCAI19/paper.tex
fixes of the last editorial feedback

\author{
Sofia Reis$^1$
\and
Rui Abreu$^1$\and
Marcelo d'Amorim$^2$\affiliations
$^1$IST, University of Lisbon \& INESC-ID, Portugal\\
$^2$Federal University of Pernambuco, Brazil\\
\emails
sofia.o.reis@tecnico.ulisboa.pt,
rui@computer.org; damorim@cin.ufpe.br\\
}

@@

\begin{wrapfigure}[8]{1}{0.25\textwidth}
  \hspace{-2ex}
  \centering
  \scriptsize
  \setlength{\tabcolsep}{3.5pt}
  \begin{tabular}{c|cccc|c}
    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
  \end{tabular}
  \caption{An example spectrum.}
  \label{fig:spectrum-example}
\end{wrapfigure}

@@

		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction in file size (percentages). Higher is better.}
	\label{tab:red}
\end{table}
\normalsize

\subsubsection{RQ2: \rqtwo}
\label{rq:2}

@@

\begin{figure}[tb]
		\vspace{-0.2cm}
		\centering
		\includegraphics[width=0.42\textwidth]{figures/boxplot.png}
		\vspace{-0.4cm}
		\caption{Distributions of $\Delta{}C$ considering all cases where \combpar{k}
        outperformed the baseline}
		\label{fig:boxplot}
		\vspace{-0.2cm}
\end{figure}

@@

	\scriptsize
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}c|c|c|c|c@{}}
     \toprule
  & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
  & SFL  & \comb\       & SFL                & \comb\              \\ \midrule
Mean  & \textbf{779.3} (584.3) & \textbf{738.2} (679.7)   &  \textbf{630.6} (516.4)    & \textbf{611.9} (614.0)   \\ \midrule
Median & \textbf{187.7} (49.4) & \textbf{167.2} (69.3)      & \textbf{167.2} (53.0) & \textbf{107.5} (56.9)\\ \midrule
Variance & \textbf{1218.3} (1223.1) & \textbf{1186.3} (1352.4)  &  \textbf{1058.4} (1148.1) &  \textbf{1048.6} (1294.9) \\ \midrule
Shapiro-Wilk &\makecell{$W$ = 0.67 \\ $p$ = 9.64 x $10^{-15}$} & \makecell{$W$ = 0.66 \\ $p$ = 5.59 x $10^{-15}$} & \makecell{$W$ = 0.63 \\ $p$ = 1.09 x $10^{-15}$} &  \makecell{$W$ = 0.63 \\ $p$ = 8.95 x $10^{-16}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 175.18 \\ p-value = 9.71 x $10^{-38}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests for $C$}
  \label{table:st}
  \end{adjustwidth}
\end{table}

@@

\begin{figure}[tb]
	\vspace{-2cm}
		\includegraphics[width=0.5\textwidth]{figures/heatmap_seg_result.png}
		\caption{Siegel post-hoc analysis results}
		\label{fig:performance}
		\vspace{-0.2cm}
\end{figure}

>>>>

\author{
Sofia Reis$^{1,2}$
\and
Rui Abreu$^{1,2}$ \textnormal{and}
Marcelo d'Amorim$^3$\affiliations
$^1$IST, University of Lisbon, Portugal\\
$^2$INESC-ID, Portugal\\
$^3$Federal University of Pernambuco, Brazil\\
\emails
sofia.o.reis@tecnico.ulisboa.pt,
rui@computer.org; damorim@cin.ufpe.br\\
}

@@

\begin{figure}[tb]
  \hspace{-2ex}
  \centering
  \scriptsize
  \setlength{\tabcolsep}{3.5pt}
  \begin{tabular}{c|cccc|c}
    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
  \end{tabular}
  \caption{An example spectrum.}
  \label{fig:spectrum-example}
\end{figure}

@@

		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction in file size (percentages). Higher is better.}
	\label{tab:red}
	    \vspace{-2ex}
\end{table}

\normalsize
\subsubsection{RQ2: \rqtwo}
\label{rq:2}

@@

\begin{figure}[tb]
		\vspace{-0.2cm}
		\centering
		\includegraphics[width=0.42\textwidth]{figures/boxplot.png}
		\vspace{-0.4cm}
		\caption{Distributions of $\Delta{}C$ considering all cases where \combpar{k}
        outperformed the baseline}
		\label{fig:boxplot}
		\vspace{-0.3cm}
\end{figure}

@@

	\scriptsize
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}c|c|c|c|c@{}}
     \toprule
  & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
  & SFL  & \comb\       & SFL                & \comb\              \\ \midrule
Mean  & \textbf{779.3} (584.3) & \textbf{738.2} (679.7)   &  \textbf{630.6} (516.4)    & \textbf{611.9} (614.0)   \\ \midrule
Median & \textbf{187.7} (49.4) & \textbf{167.2} (69.3)      & \textbf{167.2} (53.0) & \textbf{107.5} (56.9)\\ \midrule
Variance & \textbf{1218.3} (1223.1) & \textbf{1186.3} (1352.4)  &  \textbf{1058.4} (1148.1) &  \textbf{1048.6} (1294.9) \\ \midrule
Shapiro-Wilk &\makecell{$W$ = 0.67 \\ $p$ = 9.64 x $10^{-15}$} & \makecell{$W$ = 0.66 \\ $p$ = 5.59 x $10^{-15}$} & \makecell{$W$ = 0.63 \\ $p$ = 1.09 x $10^{-15}$} &  \makecell{$W$ = 0.63 \\ $p$ = 8.95 x $10^{-16}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 175.18 \\ p-value = 9.71 x $10^{-38}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests for $C$}
  \label{table:st}
  \end{adjustwidth}
  \vspace{-2ex}
\end{table}

@@

\begin{figure}[tb]
	\vspace{-2.3cm}
		\includegraphics[width=0.5\textwidth]{figures/heatmap_seg_result.png}
		\vspace{-0.6cm}
		\caption{Siegel post-hoc analysis results}
		\label{fig:performance}
		\vspace{-0.4cm}
\end{figure}
